Figures

### 2021-11-10 figures/01_geometry.Rmd
fix label overlap, add 1:1 line

```{r 01_geometry_base, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=4.8, fig.height=2.3}
# setwd("figures")
theme_opts <- cowplot::theme_cowplot() +
  theme(legend.position = "none",
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 11))
text_size <- 3

@@

rsq <- round(broom::glance(lm(dist_viscenter ~ dist_deepest, data = dt))$r.squared, 2)
gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 2550, y = 400, label = paste0("R^2 == ", rsq),
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 1800, y = 150,
    label = get_formula(
      lm(dist_viscenter ~ dist_deepest, data = st_drop_geometry(dt))),
    size = text_size - 0.85, fill = "white", label.size = NA) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  xlim(0, 3000) +
  theme_opts

@@

rsq <- round(broom::glance(lm(nearshore_slope_mean ~ inlake_slope_pnt, data = test))$r.squared, 2)
gg_slope_base <- ggplot(data = test) +
  geom_point(aes(nearshore_slope_mean, inlake_slope_pnt), size = 1) +
  geom_smooth(aes(nearshore_slope_mean, inlake_slope_pnt), method = "lm", se = FALSE) +
  geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    alpha = 1, fill = "white") +
  annotate("text", x = 0.34, y = 0.05, label = paste0("R^2 == ", rsq),
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 0.27, y = 0.01,
    label = get_formula(
      lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)),
    size = text_size - 0.85, fill = "white", label.size = NA) +
  # geom_abline(slope = 1, intercept = 0) +
  xlab("Nearshore slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "") +
  theme_opts

>>>>

```{r 01_geometry_base, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=4.8, fig.height=2.3}
# setwd("figures")
theme_opts <- cowplot::theme_cowplot() +
  theme(legend.position = "none",
    axis.text = element_text(size = 9),
    axis.title = element_text(size = 10))
text_size <- 3

@@

rsq <- round(broom::glance(lm(dist_viscenter ~ dist_deepest, data = dt))$r.squared, 2)
gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_abline(intercept = 0, slope = 1, linetype = 2, color = "darkgreen", size = 1) +
  annotate("text", x = 2550, y = 430, label = paste0("R^2 == ", rsq), # higher y is up
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 1900, y = 150, # 1800
    label = get_formula(
      lm(dist_viscenter ~ dist_deepest, data = st_drop_geometry(dt))),
    size = text_size - 1.1, fill = "white", label.size = NA) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  theme_opts +
  scale_x_continuous(expand = c(0, 0.01), limits = c(0, 3000)) +
  scale_y_continuous(expand = c(0, 1), limits = c(0, 3000))

@@

rsq <- round(broom::glance(lm(nearshore_slope_mean ~ inlake_slope_pnt, data = test))$r.squared, 2)
gg_slope_base <- ggplot(data = test) +
  geom_point(aes(nearshore_slope_mean, inlake_slope_pnt), size = 1) +
  geom_smooth(aes(nearshore_slope_mean, inlake_slope_pnt), method = "lm", se = FALSE) +
  geom_abline(intercept = 0, slope = 1, linetype = 2, color = "darkgreen", size = 1) +
  geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    alpha = 1, fill = "white") +
  annotate("text", x = 0.34, y = 0.05, label = paste0("R^2 == ", rsq),
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 0.22, y = 0.01,
    label = get_formula(
      lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)),
    size = text_size - 1.2, fill = "white", label.size = NA, label.padding = unit(0.1, "lines")) +
  xlab("Nearshore slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "") +
  theme_opts +
  scale_x_continuous(expand = c(0, 0.01), limits = c(0, NA)) +
  scale_y_continuous(expand = c(0, 0.01), limits = c(0, NA))

### 2021-11-10 manuscript/figures.Rmd
fix label overlap, add 1:1 line

```{r 01_geometry_base, fig.cap = "Comparison among proxy and true values of lake geometry for A) distance to deepest point versus distance distance to lake center and B) nearshore land slope versus in-lake slope. A best-fit line and equation is shown to shown to facilitate computation of correction factors for proxy values of lake geometry. Coefficients of determination are shown to illustrate representativeness.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_base-1.pdf")
```

>>>>

```{r 01_geometry_base, fig.cap = "Comparison among proxy and true values of lake geometry for A) distance to deepest point versus distance distance to lake center and B) nearshore land slope versus in-lake slope. A best-fit line (solid) and equation is shown to shown to facilitate computation of correction factors for proxy values of lake geometry. A 1:1 line (dashed) is shown to illustrate bias. Coefficients of determination are shown to illustrate representativeness.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_base-1.pdf")
```
